---
title: "README"
author: "Bo Li"
date: "2022/10/12"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(nycflights13)
library(dplyr)
library(ggplot2)
```

 
#### Question:
What time of day should you fly if you want to avoid delays as much as possible? Does this choice depend on anything? Season? Weather? Airport? Airline? Find three patterns (“null results” are ok!). Write your results into Rmarkdown. Include a short introduction that summarizes the three results. Then, have a section for each finding. Support each finding with data summaries and visualizations. Include your code when necessary. This shouldn’t be long, but it might take some time to find the things you want to talk about and lay them out in an orderly way.

#### time by hour
```{r}
avgdelay = flights %>%
  group_by(hour) %>%
  summarise(arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
  arrange(arr_delay) 
ggplot(data = avgdelay, aes(x= hour, y = arr_delay)) + 
  geom_bar(stat="identity") + 
  ylab('Average delay') +
  xlab('Hour')
```

The delay happends more on evening and low on morning. So people should take flights before 10am if they want to avoid delays as much as possible.




#### Destination Airport
```{r}
delay_airport= flights %>%
  group_by(dest) %>%
  summarise(n = n(), arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
  arrange(arr_delay) 
ggplot(data = delay_airport, aes(x= dest, y = arr_delay)) + 
  geom_bar(stat="identity") + 
  ylab('Average delay') +
  xlab('Destination Airport') +
  theme_grey(base_size = 8) +
  theme(axis.text.x = element_text(angle = -90))
```
From the graph, we can see ANC, LGA, PSP, SRO, and SYB have significant negative average delay time which recommenced as destination.


#### Airline
```{r}
delay_carrier= flights %>%
  group_by(carrier) %>%
  summarise(n = n(), arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
  arrange(arr_delay) 
ggplot(data = delay_carrier, aes(x= carrier, y = arr_delay)) + 
  geom_bar(stat="identity") + 
  ylab('Average delay') +
  xlab('Airline')
```

The graph demonstrate AS and HA with negative average delay, so recommend to take those carrier and avoid EV, F9, YV, and Fl.

#### Summary
To avoid the delay of flights,take flight in the morning to LGA or PSP with Alaska Airlines or Hawaiian Airlines.